Reproducibility of HCP pipelines across operating systems

### 2017-05-25 paper.tex
Added a few notes
Added not in intro
Added some indicators on subsections

\author{Lalet Scaria, Lindsay B. Lewis, Alan C. Evans, Tristan Glatard}

@@

Reproducibility has several other aspects, see, e.g.,
\url{https://medium.com/@lorenaabarba/barba-group-reproducibility-syllabus-e3757ee635cf#.ty3zmgd4k}

For an overview of variability accross analysis methods in fMRI, see \url{http://journal.frontiersin.org/article/10.3389/fnins.2012.00149/full}.

For a general overview in fMRI, see \url{http://www.nature.com/nrn/journal/vaop/ncurrent/box/nrn.2016.167_BX3.html}

@@

>>>>

\author{Lalet Scaria, Lindsay B. Lewis, Najmeh Khalili-Mahani, Alan C. Evans, Tristan Glatard}

@@

Reproducibility has several other aspects, see, e.g.,
\url{https://medium.com/@lorenaabarba/barba-group-reproducibility-syllabus-e3757ee635cf#.ty3zmgd4k}/

@@

\paragraph{Algorithms}
A brief description of the algorithms used in the script for analysis

\paragraph{Softwares and Libraries}
A brief description of the softwares and libraries used
